Evaluate PEER in each cohort and brain region

### 2020-11-18 combined_analysis/eval_resid_in_each.Rmd
Initial commit

# Store data 
storeData = function( name, file, description){
  saveRDS( eval(parse(text=name)), file=file)

@@

  PEER_setNk(model,20)

@@

  # upload latent variables
  file = paste0('metadata_',gsub(" ", '', gsub("-", "_", datID)), ".RDS")
  storeData( latentVariables, file, paste0(datID, " Latent variables for QTL analysis"))
}
```

>>>>

# Store data 
storeData = function( data, file, description){
  saveRDS( data, file=file)

@@

  PEER_setNk(model,30)

@@

  # upload latent variables
  file = paste0('PEER',gsub(" ", '', gsub("-", "_", datID)), ".RDS")
  storeData( latentVariables, file, paste0(datID, " Latent variables for QTL analysis"))
}
```
